%!TEX root = ../main.tex

\subsection{\cite{maarouf_cloud_2021} - Cloud Computing and Virtualization Security: A Survey}

\textbf{Cloud Computing and Virtualization Security: A Survey }

\subsubsection*{Abstract \cite{maarouf_cloud_2021}}

“Cloud computing is becoming one of the leading technologies to host Internet services as it offers flexibility for their customers besides being cost-effective for providers. Virtualization is a key technology for cloud computing as it allows hardware resources to distribute among several customers. The hypervisor (HV) is the controlling software that ensures effective isolation and security of the virtual systems. Despite its usefulness, cloud computing is neither trustworthy nor secure against local or remote attacks. To mitigate these threats, AMD Secure Encrypted Virtualization (AMD-SEV) and Intel Software Guard Extension (Intel-SGX) technologies were introduced as potential solutions by a hardware-assisted Trusted Execution Environment (TEE).

Our paper surveys several types of attacks done by either a compromised HV or a malicious tenant targeting SEV-encrypted and Intel SGX virtual machines to analyze the vulnerability in its design. We classify the literature by the position of the attacker and the purpose of attacking these VMs. We also survey different kinds of defense models that can mitigate the studied attacks.”

\subsubsection*{Conclusion \cite{maarouf_cloud_2021}}
“In this paper, we present a classification framework to categorize previous literature on cloud computing and virtualization security. Although we did not cover a substantial portion
of research papers, our framework can be used for a larger
survey, which we leave for future work. Our classification
is meant to help practitioners understand the threats against
their cloud services. We believe that expanding on the current
classification framework would prove useful to serve such a
purpose. ”


