%!TEX root = ../main.tex

\section{About this Document}
%\addcontentsline{toc}{section}{About this Document}

 
\subsection{Goal}
%\addcontentsline{toc}{subsection}{Goal}

The goal of this document is to provide an overview of the Confidential Compute service 
and shielded VM provided by Google Cloud (GCP). 
This document includes: 
(1) the description of the trust-layers used by Google, 
(2) links to resources, 
(3) example code and 
(4) an explicit literature research into known vulnerabilities of the AMD EPYC CPU 
that is the main hardware component of the Google Confidential Compute. 

\subsection{Content}
%\addcontentsline{toc}{subsection}{Content}

Topics discussed in this document are:
\begin{enumerate}
  \item GCP Titan (TPM)
  \item GCP Shielded VM (vTPM)
  \item GCP Confidential VM (TEE)
  \item GCP Integrity Monitoring
  \item GCP Organizational Policies
  \item GCP Combining Encryption
\end{enumerate}

\subsection{Quality Assurance}
%\addcontentsline{toc}{subsection}{Quality Assurance}

The goal is to have various Subject Matter Experts (SME) review this (Google) document 
and the Zotero reference library and provide feedback via for example adding comments. 
The only way to achieve this from a compliance viewpoint is by not including information 
from any of our clients and employers. 
In addition the context of and in a company is specific and unique 
and therefore difficult to comment on by SME’s not knowledgeable of this context.

\subsection{License}
%\addcontentsline{toc}{subsection}{License}

The content of this document is a (re-)mix of available public sources. 
The original authors are Maarten Baijs, Laurens Knoll and Edzo Botjes. 
This document includes reference to these public sources. 
The license of this document is 
Creative Commons By Association 4.0\footnote{\url{https://creativecommons.org/licenses/by-sa/4.0/}}. 
This implies that everybody is free to use, adapt and change the content of this document 
but needs to mention explicitly that this document is the source.

\subsection{Tool Support}
%\addcontentsline{toc}{subsection}{Tool Support}

\begin{enumerate}
  \item References are part of the public zotero reference group  
  \footnote{\url{https://www.zotero.org/groups/4612254/confidential_compute/library}}
  “confidential compute”.
  \item Zotero\footnote{\url{https://www.zotero.org/support/zotero_support}} 
  is an open source reference manager.
  \item Zotero has great support in 
  academia\footnote{\url{https://libguides.caltech.edu/introacademicwriting/zotero}}\textsuperscript{,}\footnote{\url{https://www.apa.org/science/about/psa/2013/12/reference-manager}}.
  \item This is a description on how to use Zotero in combination with
  google docs\footnote{\url{https://www.zotero.org/support/google_docs}}.
  \item This document is maintained as 
  GitHub Project\footnote{\url{https://github.com/binxio/gcp-conf-compute-analysis}}.\\ 
  Feel free to contribute via code or discussion.
\end{enumerate}

